SST_patterns

### 2020-01-24 SST_patterns.Rmd
Update

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals, colour = product)) +
geom_point(aes(size = distance)) +
geom_smooth(method = "lm", size = 1.2)

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals, colour = product)) +
geom_bubble(aes(size = distance)) +
geom_smooth(method = "lm", size = 1.2)

@@

@@

@@

>>>>

ggplot(data = Combined_frequency, aes(x = t, y = number_of_signals, colour = product)) +
geom_point(aes(size = distance)) +
geom_smooth(method = "lm", size = 1.2)+
theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

@@

  ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_line(aes(colour = distance)) +
  geom_point(aes(colour = distance)) +
  geom_smooth(aes(colour = distance), method = "lm") +
  # labs(x = NULL) +
  facet_wrap(~site) #+
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

@@

ggplot(Combined_frequency, aes(x=date, y=number_of_signals, size=distance, color=product)) +
  geom_point(alpha=0.5) +
  facet_wrap(~site) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

@@

# Histogram

combined_frequency_season <- Combined_frequency %>% 
  mutate(month = month(date, abbr = T, label = T),
         year = year(date)) %>% 
  mutate(season = ifelse(month %in% c("Jan", "Feb", "Mar"), "Summer",        
                           ifelse(month %in% c("Apr", "May", "Jun"), "Autumn",
                                ifelse(month %in% c("Jul", "Aug", "Sep"), "Winter",
                                       ifelse(month %in% c("Oct", "Nov", "Dec"), "Spring","Error")))))

CMC_dur <- read_excel("Data/CMC_dur.xlsx")

ggplot(data = CMC_dur, aes(x = duration)) +
  geom_histogram(aes(fill = product)) +
  facet_wrap(~site)
